---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidychat)
library(dplyr)
set_tidychat("*", "127.0.0.1", 7890)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# What's TidyChat

Inspired by @jcrodriguez1989's chatgpt package, a chatgpt library directly chat with what you write!

## Installation

You can install the development version of {tidychat} from [GitHub](https://github.com/jiayaobo/tidychat) with:

``` r
# install.packages("remotes")
remotes::install_github("jiayaobo/tidychat")
```

## Requirements

See what @jcrodriguez1989 describes in [Requirements](https://github.com/jcrodriguez1989/chatgpt)

You can set your config with

``` r
set_tidychat(openai_api_key,
             proxy_url = NULL,
             proxy_port = NULL,
             openai_model = "gpt-3.5-turbo",
             openai_max_tokens = 256,
             openai_temperature = 1,
             openai_top_p = 1,
             openai_frequency_penalty = 0,
             openai_presence_penalty = 0,
             openai_verbose = TRUE,
             openai_return_language = "English")
```

For examples, if you're using a proxy, like using clashx pro which use your 7890 port, you can set the proxy with

``` r
set_tidychat(openai_api_key="your key",
             proxy_url = "127.0.0.1",
             proxy_port = 7890,
             openai_model = "gpt-3.5-turbo",
             openai_max_tokens = 256,
             openai_temperature = 1,
             openai_top_p = 1,
             openai_frequency_penalty = 0,
             openai_presence_penalty = 0,
             openai_verbose = TRUE,
             openai_return_language = "English")
```

## Features

-   You can ask chatgpt for any questions with pure character string

-   You can explore your data with tidychat

-   You can get a report of summary without effort

-   You can get the solution for your processing programming

-   Integrate with %\>%

## Simply Ask GPT

-   Character

```{r, results='asis'}
askgpt("Do you know Renmin University of China?") %>% cat
```

-   Function

```{r, results='asis'}
find_prime <- function(x) {
  # find primary number
}

find_prime %>% askgpt("compelete the function to find primes between 1 to x") %>% cat
```

-   Sequence Functions

```{r, results='asis'}
fseq <- .%>% filter(A>10) %>% mutate(B=A*10) %>% lm(A~B, data=.) %>% summary
fseq %>% askgpt("describe what the function do?") %>% cat
```

-   Data

```{r, results='asis'}
data("mtcars")
mtcars %>% askgpt("give me some description on it") %>% cat
```

-   Or Data Related Summary

```{r, results='asis'}
data("mtcars")
mtcars %>% lm(mpg~disp, data=.) %>% summary %>% askgpt("report the summay to me!") %>% cat
```

## Guidance on Analysing Data

-   For Data.Frame

```{r, results='asis'}
data("mtcars")
mtcars %>% analyse("make regression between mpg and other variables") %>% cat
```

-   For Table

```{r, results='asis'}
smoking <- c("yes", "no", "yes", "no", "yes", "no", "yes", "no", "yes", "no")
lung_cancer <- c("yes", "no", "yes", "no", "no", "no", "yes", "yes", "yes", "yes")

lung_data <- data.frame(smoking, lung_cancer)
lung_data$smoking_desc <- ifelse(lung_data$smoking == "yes", "Smoker", "Non-smoker")
lung_data$lung_cancer_desc <- ifelse(lung_data$lung_cancer == "yes", "Diagnosed with lung cancer", "No lung cancer")
cont_table <- table(lung_data$smoking_desc, lung_data$lung_cancer_desc)


cont_table %>% analyse("check if smoking and lung cancer are related") %>% cat
```

## Create Reports With Format

-   HTest

```{r, results='asis'}
# create the contingency table
lung_cancer <- matrix(c(90, 10, 110, 40), ncol = 2, byrow = TRUE)
colnames(lung_cancer) <- c("Diagnosed with lung cancer", "No lung cancer")
rownames(lung_cancer) <- c("Non-smoker", "Smoker")

# perform the chi-squared test
chisq.test(lung_cancer) %>% create_report %>% cat
```

-   For Summary.\*

```{r, results='asis'}
mtcars %>% lm(mpg~disp, data=.) %>% summary %>% create_report %>% cat
```

## Code Completion

```{r, results='asis'}
f <- function(x, y) {
  # merge two sorted list x and y
}
f %>% code_completion(idea=NULL) %>% cat
```

## Code Comment

```{r, results='asis'}
fibo <- function(n){
  if (n == 1 || n == 0 || n == 2){
    return(n)
  }else {
    return(fibo(n-1) + fibo(n-2))
  }
}
fibo %>% code_comment %>% cat
```

## Others

### Disable Console Messages

If you want {tidychat} not to show messages in console,just like {chatgpt}, set the environment variable `OPENAI_VERBOSE=FALSE`.

### Change the language of ChatGPT responses

Change the `OPENAI_RETURN_LANGUAGE` with \``Sys.setenv`

```{r, results='asis'}
Sys.setenv("OPENAI_RETURN_LANGUAGE" = "中文")
# check if modified
get_tidychat()
```

```{r, results='asis'}
mtcars %>% lm(mpg~disp, data=.) %>% summary %>% create_report %>% cat
```

### References

[chatgpt](https://github.com/jcrodriguez1989/chatgpt)

### Todo

-  [ ] Add llama model support
-  [ ] Add generic functions for `ggplot` class