---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library("tidychat")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# What's TidyChat 

Inspired by @jcrodriguez1989's chatgpt package, a chatgpt library directly chat with what you write!

## Installation

You can install the development version of {tidychat} from [GitHub](https://github.com/jiayaobo/tidychat) with:

``` r
# install.packages("remotes")
remotes::install_github("jiayaobo/chatgpt")
```

## Requirements

See what @jcrodriguez1989 describes in [Requirements](https://github.com/jcrodriguez1989/chatgpt)

You can set your config with

``` r
set_tidychat(openai_api_key,
                         proxy_url = NULL,
                         proxy_port = NULL,
                         openai_model = "gpt-3.5-turbo",
                         openai_max_tokens = 256,
                         openai_temperature = 1,
                         openai_top_p = 1,
                         openai_frequency_penalty = 0,
                         openai_presence_penalty = 0,
                         openai_verbose = TRUE,
                         openai_return_language = "English")
```

## Features 

* You can ask chatgpt for any questions with pure character string

* You can explore your data with tidychat

* You can get a report of summary without effort

* You can get the solution for your processing programming

* Integrate with %>%

## Simply Ask GPT

**Sorry, I have no idea why generic functions for character is failed for askgpt :(**

* Character

```{r, echo=FALSE, results='asis'}
askgpt.character("how do you like Renmin University of China?") %>% cat
```
* Function
```{r, echo=FALSE, results='asis'}
find_prime <- function(x) {
  # find primary number
}
find_prime %>% askgpt("compelete the function to find primes between 1 to x") %>% cat
```

## Additional Parameters

### Disable Console Messages

If you want {chatgpt} not to show messages in console, please set the environment variable `OPENAI_VERBOSE=FALSE`.

### Addin Changes in Place

If you want {chatgpt} addins to take place in the editor -i.e., replace the selected code with the result of the addin execution- then you sould set the environment variable `OPENAI_ADDIN_REPLACE=TRUE`.

### Change the language of ChatGPT responses

To change the language that ChatGPT responds in, the `OPENAI_RETURN_LANGUAGE` environment variable must be changed.
E.g., 

```{r}
Sys.setenv("OPENAI_RETURN_LANGUAGE" = "Español")
cat(chatgpt::explain_code("for (i in 1:10) {\n  print(i ** 2)\n}"))
```

### ChatGPT Model Tweaks

As default:

* `OPENAI_MODEL`; defaults to `"gpt-3.5-turbo"`
* `OPENAI_MAX_TOKENS`; defaults to `256`
* `OPENAI_TEMPERATURE`; defaults to `1`
* `OPENAI_TOP_P`; defaults to `1`
* `OPENAI_FREQUENCY_PENALTY`; defaults to `0`
* `OPENAI_PRESENCE_PENALTY`; defaults to `0`

### References

[chatgpt](https://github.com/jcrodriguez1989/chatgpt)
